Magnetized accretion disks around Kerr black holes with scalar hair

### 2017-11-29 kbhssh_disks/paper_prd.tex
bibliography fixed

\documentclass[aps, prl, amsmath, floats,floatfix, twocolumn, superscriptaddress, nofootinbib, 
showpacs]{revtex4}

@@

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{epsfig}
\usepackage{color}
\usepackage{graphicx,subfigure}
\usepackage{units}
\usepackage{slashbox}

@@

We use the stationary and axisymmetric metric ansatz provided by\citet{Herdeiro:2014a}

@@

\subsection{Magnetized disks}
We use the procedure described by~\citet{Montero:2007}, where we write the equations of ideal general relativistic MHD are the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and 
$\nabla_{\mu} (\rho u^{\mu}) = 0$, 
where $\nabla_{\mu}$ is the covariant derivative and
\begin{equation}\label{eq:e-m_tensor}
T^{\mu\nu} = (\rho h + b^2)u^{\mu}u^{\nu} + \left(p + \frac{1}{2}b^2\right)g^{\mu\nu} - b^{\mu}b^{\nu},
\end{equation}
is the energy-momentum tensor of a magnetised perfect fluid, $h$, $\rho$ $p$ being the fluid specific enthalpy, density and fluid pressure, respectively. 
Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow. Contracting the divergence of Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\,\,\beta} = \delta^{\alpha}_{\,\,\beta} + u^{\alpha}u_{\beta}$, we arrive at
\begin{equation}
(\rho h + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
\end{equation}
where $i = r, \theta$. Then, we rewrite this equation in terms of the specific angular momentum $l$ and of the angular velocity $\Omega$, to obtain
\begin{equation}\label{eq:diff_ver}
\partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{w} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}w} = 0\,,
\end{equation}
where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.
To integrate Eq.~\eqref{eq:diff_ver} we first assume a polytropic equation of state of the form
\begin{equation}\label{eq:eos_fluid}
p = K \rho^{\Gamma},
\end{equation}
with $K$ and $\Gamma$ constants.
Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$, and introduce the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, in order to write an analogue equation to Eq.~\eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$~\citep{Komissarov:2006}
\begin{equation}\label{eq:eos_mag_tilde}
\tilde{p}_{\mathrm{m}} = M \tilde{w}^q,
\end{equation}
or, in terms of the magnetic pressure $p_{\mathrm{m}}$
\begin{equation}\label{eq:eos_mag}
p_{\mathrm{m}} = M \mathcal{L}^{q-1} w^q,
\end{equation}
where $w = \rho h$ is the fluid enthaply density, and $M$ and $q$ are constants.
If we define the potential as $W \equiv \ln u_t|$, then we can integrate the equation~\eqref{eq:diff_ver} as

@@

It is relevant to note that we could have used the framework described by~\citet{Komissarov:2006}. As we will show in appendix~\ref{komissarov_appendix}, we do not take this approach because it is not appropriate for some cases of KBHsSH.

@@

\bibliographystyle{apsrev}
\bibliography{references}

@@

In the figures \ref{comparison_alt_mag_1}, \ref{comparison_alt_mag_2}, \ref{comparison_alt_mag_3}, \ref{comparison_alt_radial_1}, \ref{comparison_alt_radial_2}, \ref{comparison_alt_radial_3} we show the comparison between the results for KBHsSH using \citet{Montero:2007} and \citet{Komissarov:2006}. The figures show good agreement for the highly magnetized case ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$) but not quite for the non-magnetized and mildly magnetized cases, especially for the model III. This is due to the $h = 1$ approximation breaking down. In the table~\ref{table:pot} we show the correlation between the value of the potential at the centre and the specific enthalpy at the centre. It is easy to note that for higher absolute values of $W_{\mathrm{c}}$ we get values of $h_{\mathrm{c}}$ further away from the case $h = 1$. This is interesting because these high values of $W_{\mathrm{c}}$ (particularly the one for the model III) is unattaniable for any KBH (as is shown by~\citet{Abramowicz:1978}, the maximum value of $W_{\mathrm{c}}$ for a KBH is $W_{\mathrm{c}} = 0.549$).

@@

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig2_III_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig2_III_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig2_III_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig2_III_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig2_III_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig2_III_K__3.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution for the model I. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
\label{comparison_alt_mag_1}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig3_IV_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig3_IV_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig3_IV_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig3_IV_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig3_IV_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig3_IV_K__3.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution for the model II. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
\label{comparison_alt_mag_2}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig4_V_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig4_V_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig4_V_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig4_V_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig4_V_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig4_V_K__3.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution for the model III. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
\label{comparison_alt_mag_3}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.3]{figures/radial_III_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_III_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_III_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_III_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_III_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_III_K__3.pdf}
\hspace{-0.2cm}
\caption{Radial rest-mass density distribution for the model I at the equatorial plane. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
\label{comparison_alt_radial_1}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.3]{figures/radial_IV_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_IV_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_IV_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_IV_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_IV_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_IV_K__3.pdf}
\hspace{-0.2cm}
\caption{Radial rest-mass density distribution for the model II at the equatorial plane. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
\label{comparison_alt_radial_2}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.3]{figures/radial_V_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_V_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_V_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_V_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_V_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_V_K__3.pdf}
\hspace{-0.2cm}
\caption{Radial rest-mass density distribution for the model III at the equatorial plane. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\citet{Montero:2007} and the right column correspond to the~\citet{Komissarov:2006} approximation.}
\label{comparison_alt_radial_3}
\end{figure*}
\end{appendix}

>>>>

\documentclass[twocolumn,aps,showpacs,showkeys,prd,superscriptaddress,byrevtex, amsmath]{revtex4-1}

@@

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{epsfig}
\usepackage{color}
\usepackage{graphicx,subfigure}
\usepackage{units}
\usepackage{slashbox}
\usepackage{aas_macros}

@@

We use the stationary and axisymmetric metric ansatz provided by\cite{Herdeiro:2014a}

@@

\subsection{Magnetized disks}
We use the procedure described by~\cite{Montero:2007}, where we write the equations of ideal general relativistic MHD are the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and 
$\nabla_{\mu} (\rho u^{\mu}) = 0$, 
where $\nabla_{\mu}$ is the covariant derivative and
\begin{equation}\label{eq:e-m_tensor}
T^{\mu\nu} = (\rho h + b^2)u^{\mu}u^{\nu} + \left(p + \frac{1}{2}b^2\right)g^{\mu\nu} - b^{\mu}b^{\nu},
\end{equation}
is the energy-momentum tensor of a magnetised perfect fluid, $h$, $\rho$ $p$ being the fluid specific enthalpy, density and fluid pressure, respectively. 
Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow. Contracting the divergence of Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\,\,\beta} = \delta^{\alpha}_{\,\,\beta} + u^{\alpha}u_{\beta}$, we arrive at
\begin{equation}
(\rho h + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
\end{equation}
where $i = r, \theta$. Then, we rewrite this equation in terms of the specific angular momentum $l$ and of the angular velocity $\Omega$, to obtain
\begin{equation}\label{eq:diff_ver}
\partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{w} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}w} = 0\,,
\end{equation}
where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.
To integrate Eq.~\eqref{eq:diff_ver} we first assume a polytropic equation of state of the form
\begin{equation}\label{eq:eos_fluid}
p = K \rho^{\Gamma},
\end{equation}
with $K$ and $\Gamma$ constants.
Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$, and introduce the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, in order to write an analogue equation to Eq.~\eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$~\citep{Komissarov:2006}
\begin{equation}\label{eq:eos_mag_tilde}
\tilde{p}_{\mathrm{m}} = M \tilde{w}^q,
\end{equation}
or, in terms of the magnetic pressure $p_{\mathrm{m}}$
\begin{equation}\label{eq:eos_mag}
p_{\mathrm{m}} = M \mathcal{L}^{q-1} w^q,
\end{equation}
where $w = \rho h$ is the fluid enthaply density, and $M$ and $q$ are constants.
If we define the potential as $W \equiv \ln u_t|$, then we can integrate the equation~\eqref{eq:diff_ver} as

@@

It is relevant to note that we could have used the framework described by~\cite{Komissarov:2006}. As we will show in appendix~\ref{komissarov_appendix}, we do not take this approach because it is not appropriate for some cases of KBHsSH.

@@

\bibliography{references.bib}

@@

In the figures \ref{comparison_alt_mag_1}, \ref{comparison_alt_mag_2}, \ref{comparison_alt_mag_3}, \ref{comparison_alt_radial_1}, \ref{comparison_alt_radial_2}, \ref{comparison_alt_radial_3} we show the comparison between the results for KBHsSH using \cite{Montero:2007} and \cite{Komissarov:2006}. The figures show good agreement for the highly magnetized case ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$) but not quite for the non-magnetized and mildly magnetized cases, especially for the model III. This is due to the $h = 1$ approximation breaking down. In the table~\ref{table:pot} we show the correlation between the value of the potential at the centre and the specific enthalpy at the centre. It is easy to note that for higher absolute values of $W_{\mathrm{c}}$ we get values of $h_{\mathrm{c}}$ further away from the case $h = 1$. This is interesting because these high values of $W_{\mathrm{c}}$ (particularly the one for the model III) is unattaniable for any KBH (as is shown by~\cite{Abramowicz:1978}, the maximum value of $W_{\mathrm{c}}$ for a KBH is $W_{\mathrm{c}} = 0.549$).

@@

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig2_III_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig2_III_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig2_III_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig2_III_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig2_III_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig2_III_K__3.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution for the model I. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
\label{comparison_alt_mag_1}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig3_IV_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig3_IV_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig3_IV_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig3_IV_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig3_IV_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig3_IV_K__3.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution for the model II. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
\label{comparison_alt_mag_2}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig4_V_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig4_V_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig4_V_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig4_V_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.2]{figures/fig4_V_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.2]{figures/fig4_V_K__3.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution for the model III. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
\label{comparison_alt_mag_3}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.3]{figures/radial_III_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_III_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_III_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_III_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_III_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_III_K__3.pdf}
\hspace{-0.2cm}
\caption{Radial rest-mass density distribution for the model I at the equatorial plane. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
\label{comparison_alt_radial_1}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.3]{figures/radial_IV_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_IV_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_IV_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_IV_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_IV_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_IV_K__3.pdf}
\hspace{-0.2cm}
\caption{Radial rest-mass density distribution for the model II at the equatorial plane. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
\label{comparison_alt_radial_2}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.3]{figures/radial_V_HBH_3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_V_K_3.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_V_HBH_0.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_V_K_0.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.3]{figures/radial_V_HBH__3.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.3]{figures/radial_V_K__3.pdf}
\hspace{-0.2cm}
\caption{Radial rest-mass density distribution for the model III at the equatorial plane. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
\label{comparison_alt_radial_3}
\end{figure*}
\end{appendix}
